He Said What Now?!: Predicting Interest in the Term *China Virus* by State

### 2020-05-06 Final-Draft.Rmd
changes

```{r, message=FALSE, include=FALSE}
g1 <- mcmc_dens(RM_model, pars = "sigma") + 
  labs(x = expression(sigma[w])) +
  lims(x=c(5, 25))
g2 <- mcmc_dens(RM_model, 
  pars = "Sigma[State:(Intercept),(Intercept)]", transformations = sqrt) + 
  labs(x = expression(sigma[b])) +
   lims(x=c(5, 25))
grid.arrange(g1,g2,ncol=2)
```

@@

@@

### 5.2 Table

@@

### 5.2a Model 3 is the best

@@

```{r}
head(data.frame(summary(model_3)),-2)
```

>>>>

```{r, message=FALSE, include=TRUE}
g1 <- mcmc_dens(RM_model, pars = "sigma") + 
  labs(x = expression(sigma[w])) +
  lims(x=c(5, 25))
g2 <- mcmc_dens(RM_model, 
  pars = "Sigma[State:(Intercept),(Intercept)]", transformations = sqrt) + 
  labs(x = expression(sigma[b])) +
   lims(x=c(5, 25))
grid.arrange(g1,g2,ncol=2)
```

@@

```{r}
NR_model
```

@@

@@

### 5.2 Model 3 is the best

@@

```{r}
head(data.frame(summary(model_3)))
```
